\section{CV OF THE EXPERIENCED RESEARCHER}
\label{sec:cv}

\setlength{\parindent}{0cm}{

\subsection{PERSONAL INFORMATION}

\emph{Name}: Guillaume Lema\^itre \\
\emph{Date of birth}: 27\textsuperscript{th} April 1988, 28 years old \\
\emph{Personal website}: \texttt{https://sites.google.com/site/glemaitre58} \\

\subsection{EDUCATION}

\begin{table}[!h]
\begin{tabular}{p{4cm} p{13cm}}
 \\
\textbf{07/2012 --- 12/2016} & \textbf{Co-joint PhD in Medical Imaging} \\
& \textit{``Computer Aided Diagnosis system for prostatic biopsy guidance and follow-up fusing multi-modal imaging''} \\
& Supervised by Dr. R. Mart\'i, Prof. F. M\'eriaudeau, Dr. J. Freixenet, and Dr. P. M. Walker \\
& ViCOROB, Universitat de Girona --- LE2I, Universit\'e de Bourgogne \\[.5em]  \\
\textbf{09/2012 --- 09/2014} & \textbf{Master in Business Innovation and Technology Management} \\
& \textit{``Valorisation of computerized technology in the health care sector''} \\
& Supervised by Dr. A. Bikfalvi and Dr. J. Llach \\
& Universitat de Girona \\[.5em]  \\
\textbf{09/2009 --- 06/2011} & \textbf{Master of Excellence Erasmus Mundus in Vision and Robotics} \\
& \textit{``Absolute Quantification in 1H MRSI of the Prostate at 3.0 T''} \\
& Supervised by Dr. P. M. Walker \\
& Universit\'e de Bourgogne, Universitat de Girona, Heriot-Watt University \\[.5em]  \\
\textbf{09/2016 --- 09/2009} & \textbf{Bachelor Eng. Electronic, Signal, and Image} \\
& Universit\'e de Bourgogne \\[.5em]  \\
\end{tabular}
\end{table}

\subsection{WORKING EXPERIENCE}

\begin{table}[!h]
\begin{tabular}{p{4cm} p{13cm}}
 \\
\textbf{03/2015 --- 03/2016} & \textbf{Assistant professor (ATER)} \\
& 184 hours of lecturing in databases, pattern recognition and machine learning, programming, image processing \\
& Universit\'e de Bourgogne \\[.5em]  \\
\textbf{06/2011 --- 06/2012} & \textbf{R\&D researcher} \\
& Barcelona Digital --- ViCOROB, Universitat de Girona \\[.5em]  \\
\end{tabular}
\end{table}

\newpage

\subsection{FELLOWSHIPS}

\begin{table}[!h]
\begin{tabular}{c p{14cm}}
2012 & \textbf{OMJ Grant}, Minit\`ere Fran\c cais des Affaires Etrang\`eres et Europ\'eennes, France\\
2012 & \textbf{FI-DGR PhD Grant}, Generalitat de Catalunya - AGAUR, Spain\\
2011 & \textbf{Research Master Scholarship}, Burgundy Region, France\\
2010 & \textbf{Erasmus Spanish Scholarship}, Spanish Ministry, Spain\\
2010 & \textbf{Merit-based Scholarship}, French Ministry, France\\
2010 & \textbf{Merit-based Scholarship dedicated to Research Masters}, Burgundy Region, France\\
2009 & \textbf{Spanish Ministry Mobility Scholarship}, Spanish Ministry, Spain\\
2009 & \textbf{Merit-based Scholarship}, French Ministry, France\\
2009 & \textbf{Erasmus French Scholarship}, French Ministry, France\\
2009 & \textbf{Mobility Grant}, Burgundy Region, France\\
2009 & \textbf{Region Mobility Scholarship}, Burgundy Region, France\\
2009 & \textbf{Rotary Scholarship}, Rotary Club Le Creusot, France\\
2009 --- 2011 & \textbf{Erasmus Mundus Grant}, Heriot-Watt University, Universitat de Girona, Universit\'e de Bourgogne, Scotland, Spain, France\\
2008 & \textbf{Erasmus French Scholarship}, French Ministry, France\\
2008 & \textbf{Mobility Grant}, Burgundy Region, France
\end{tabular}
\end{table}

\subsection{AWARDS}

\begin{table}[!h]
\begin{tabular}{c p{14cm}}
July, 2008 & \textbf{Student Autonomous Underwater Competition - Europe}, Nessie III - Heriot-Watt University \\
July, 2008 & \textbf{THALES Special Award for innovation}, Nessie III - Heriot-Watt University
\end{tabular}
\end{table}

\subsection{PARTICIPATION IN PUBLIC-FUNDED PROJECTS}

\begin{itemize}
\item Temporal analysis and automatic detection of lesions in multi-modal images (IA-BioBreast)
\item Identification of retinal deseases on OCT images (PHC MERLION)
\item Erasmus+ educational project (Early Mastery)
\end{itemize}

\subsection{TEACHING}

\begin{table}[!h]
\begin{tabular}{c p{13cm}}
\textbf{24 h} & \textbf{Medical Imaging: Segmentation and registration methods} \\
& Master Erasmus Mundus ViBOT \\
& Universitat de Girona \\
\textbf{24 h} & \textbf{Pattern Recognition and Machine Learning} \\
& Master Erasmus Mundus ViBOT, \texttt{https://github.com/ViBOT-Erasmus/B31XI-SI-Syllabus} \\
& Universit\'e de Bourgogne  \\
\textbf{48 h} & \textbf{Introduction to image processing} \\
& Master Erasmus Mundus ViBOT \\
& Universit\'e de Bourgogne  \\
\textbf{16 h} & \textbf{Software engineering} \\
& Master Erasmus Mundus ViBOT \\
& Universit\'e de Bourgogne   \\
\textbf{74 h} & \textbf{Introduction to databases} \\
& Bachelor of Electrical Engineering \\
& Universit\'e de Bourgogne  \\
\end{tabular}
\end{table}

\subsection{COMMUNICATION}

\begin{itemize}
\item Chair and actor in regular internal seminars at the Universit\'e de Bourgogne (RE-COOP)
\item Chair of regular scientific reading groups
\item Chair for Doctoral Day at the Universit\'e de Bourgogne (\texttt{http://le2i.github.io/doctoral-day-2015/})
\end{itemize}

\subsection{SUPERVISION}

\begin{itemize}
\item Supervision of 1 MSc. student during is master thesis in computer vision
\item Supervision of 3 BSc. and MSc. students during their summer internships
\end{itemize}

\subsection{PUBLICATIONS}

\underline{\textit{Peer-Review Journals Papers:}}

\begin{enumerate}

\item \textbf{K. Alsaih, G. Lemaitre, J. Massich, M. Rastgoo, D. Sidibe, and F. Meriaudeau}, ``Machine Learning Techniques for DME Classification on SD-OCT images'', \textit{BioMedical Engineering OnLine}, Submitted.
\item \textbf{G. Lemaitre, R. Marti, M. Rastgoo, J. Massich, F. Freixenet, J. C. Vilanova, and F. Meriaudeau}, ``Automatic prostate cancer detection through DCE-MRI images: all you need is a good normalization'', \textit{Medical Image Analysis}, Submitted.
\item \textbf{I. P. Houben, P. Van de Voorde, C. R. Jeukens, J. E. Wildberger, G. Lemaitre, I. A. Illan, A. Meyer-Baese, L. F. Kooreman, M. L. Smidt, and M. B. Lobbes}, ``Contrast-enhanced spectral mammography as work-up tool in patients recalled from breast cancer screening: risks versus benefits'', \textit{European Radiology}, Submitted.
\item \textbf{G. Lemaitre, F. Nogueira, and C. Aridas}, ``Imbalanced-learn: A Python Toolbox to Tackle the Curse of Imbalanced Datasets in Machine Learning'', \textit{Journal of Machine Learning Research}, Submitted.
\item \textbf{D. Sidibe, S. Sankar, G. Lemaitre, M. Rastgoo, J. Massich, C. Y. Cheung, G. S. Tan, D. Milea, E. Lamoureux, T. Y. Wong, and F. Meriaudeau}, ``D. Sidibe, S. Sankar, G. Lemaitre, M. Rastgoo, J. Massich, C. Y. Cheung, G. S. Tan, D. Milea, E. Lamoureux, T. Y. Wong, and F. Meriaudeau'', \textit{Computer Methods and Programs in Biomedicine}, Submitted.
\item \textbf{G. Lemaitre, M. Rastgoo, J. Massich, C. Y. Cheung, T. Y. Wong, E. Lamoureux, D. Milea, F. Meriaudeau, and D. Sidibe}, ``Classification of SD-OCT Volumes using Local Binary Patterns: Experimental Validation for DME detection'', \textit{Journal of Ophthalmology}, vol. 2016, Mai 2016.
\item \textbf{M. Belkacemi, C. Stolz, A. Mathieu, G. Lemaitre, J. Massich, and O. Aubreton}, ``Non Destructive Testing based on a Scanning-From-Heating approach: Application to non-through Defect Detection and Fiber Orientation Assessment'', \textit{Journal of Electronic Imaging}, vol. 24(6), pp 1-8, Nov/Dec 2015.
\item \textbf{G. Lemaitre, R. Marti, J. Freixenet, J. C. Vilanova, P. M. Walker, and F. Meriaudeau}, ``Computer-Aided Detection and Diagnosis for prostate cancer based on mono and multi-parametric MRI: A Review'', \textit{Computer in Biology and Medicine}, vol. 60, pp 8 - 31, 2015.
\end{enumerate}

\underline{\textit{Peer-Review International Conferences Papers:}}

\begin{enumerate}
\item \textbf{J. Massich, M. Rastgoo, G. Lemaitre, C. Cheung, T. Y. Wong, D. Sidibe, and F. Meriaudeau}, ``Classifying DME vs normal SD-OCT volumes: A review'', \textit{23\textsuperscript{rd} International Conference on Pattern Recognition (ICPR) 2016}. Cancun: Mexico (December 2016).
\item \textbf{K. Alsaih, G. Lemaitre, J. Massich, M. Rastgoo, D. Sidibe, T. Y. Wong, E. Lamoureux, D. Milea, C. Leung, and F. Meriaudeau}, ``Classification of SD-OCT volumes with multi-pyramids, LBP and HoG descriptors: Application to DME detection'', \textit{38\textsuperscript{th} International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC) 2016}. Orlando: USA (August 2016).
\item \textbf{A. Pampouchidou, K. Marias, M. Tsiknakis, P. Simos, F. Yang, G. Lemaitre, and F. Meriaudeau}, ``Video-based depression detection using local curvelet binary patterns in pairwise orthogonal planes'', \textit{38\textsuperscript{th} International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC) 2016}. Orlando: USA (August 2016).
\item \textbf{S. Hoffmann, M. Lobbes, I. Houben, K. Pinker-Domenig, G. Wengert, B. Burgeth, U. Meyer-Baese, G. Lemaitre, and A. Meyer-Baese}, ``Computer-aided diagnosis of diagnostically challenging lesions in breast MRI: a comparison between a radiomics and a feature-selective approach'', \textit{SPIE Commercial+ Scientific Sensing and Imaging}. Baltimore: USA (July 2016).
\item \textbf{M. Belkacemi, C. Stolz, A. Mathieu, G. Lemaitre, and O. Aubreton}, ``A combined three-dimensional digitisation and subsurface defect detection data using active infrared thermography'', \textit{13\textsuperscript{th} Quantitative Infrared Thermography Conference (QIRT)}. Gdansk: Poland (July 2016).
\item \textbf{M. Belkacemi, J. Massich, G. Lemaitre, C. Stolz, V. Daval, G. Pot, O. Aubreton, R. Collet, and F. Meriaudeau}, ``Wood fiber orientation assessment based on punctual laser beam excitation: A preliminary study'', \textit{13\textsuperscript{th} Quantitative Infrared Thermography Conference (QIRT)}. Gdansk: Poland (July 2016).
\item \textbf{M. Rastgoo, G. Lemaitre, J. Massich, O. Morel, F. Marzani, R. Garcia, and F. Meriaudeau}, ``Study of Data Imbalancing for Melanoma Classification'', \textit{3\textsuperscript{rd} International Conference on BIOIMAGING}. Rome: Italy (February 2016).
\item \textbf{G. Lemaitre, M. Rastgoo, J. Massich, J. C. Vilanova, P. M. Walker, J. Freixenet, A. Meyer-Baese, F. Meriaudeau, and R. Marti}, ``Normalization of T2W-MRI prostate images using Rician a priori'', \textit{SPIE Medical Imaging 2016}. San Diego: USA (February 2016).
\item \textbf{M. Rastgoo, G. Lemaitre, O. Morel, J. Massich, F. Marzani, R. Garcia, and D. Sidibe}, ``Classification of melanoma lesions using sparse coded features and random forests'', \textit{SPIE Medical Imaging 2016}. San Diego: USA (February 2016).
\item \textbf{A. Meyer-Baese, J. Massich, G. Lemaitre, and M. Rastgoo}, ``Real-Time Optical Flow with Theoretically Justified Warping Applied to Medical Imaging'', \textit{Breast Image Analysis Workshop (BIA), Medical Image Computing and Computer Assisted Interventions (MICCAI) 2015}. Munich: Germany (Oct. 2015).
\item \textbf{J. Massich, G. Lemaitre, J. Marti and F. Meriaudeau}, ``An Optimization Approach to Segment Breast Lesions in Ultra-Sound Images using Clinically Validated Visual Cues'', \textit{Breast Image Analysis Workshop (BIA), Medical Image Computing and Computer Assisted Interventions (MICCAI) 2015}. Munich: Germany (Oct. 2015).
\item \textbf{G. Lemaitre, M. Rastgoo, J. Massich, S. Sankar, F. Meriaudeau, and D. Sidibe}, ``Classification of SD-OCT volumes with LBP: Application to DME detection'', \textit{Ophthalmic Medical Image Analysis Workshop (OMIA), Medical Image Computing and Computer Assisted Interventions (MICCAI) 2015}. Munich: Germany (Oct. 2015).
\item \textbf{J. Massich, G. Lemaitre, J. Marti, and F. Meriaudeau}, ``Brest Ultra-Sound image Segmentation: an Optimization approach based on super-pixels and high-level descriptors'', \textit{International Conference on Quality Control and Artificial Vision (QCAV) 2015}. Le Creusot: France (Jun. 2015).
\item \textbf{G. Lemaitre, J. Massich, R. Marti, J. Freixenet, J. C. Vilanova, P. M. Walker, D. Sidibe, and F. Meriaudeau}, ``A Boosting Approach for Prostate Cancer Detection using Multi-parametric MRI'', \textit{International Conference on Quality Control and Artificial Vision (QCAV) 2015}. Le Creusot: France (Jun. 2015).
\item \textbf{G. Lemaitre, A. Bikfalvi, J. Llach, J. Massich, and F. Julian}, ``Business Model Design for University Technology Valorisation'', \textit{International Technology, Education and Development Conference (INTED) 2015}. Madrid: Spain (Mar. 2015).
\item \textbf{M. Rastgoo, G. Lemaitre, X. Rafael, F. Miralles, and P. Casale}, ``Pruning AdaBoost for Continuous Sensors Mining Applications'', \textit{Ubiquitous Data Mining Workshop, 20th European Conference in Artificial Intelligence 2012}. Montpellier: France (Aug. 2012).
\item \textbf{G. Lemaitre, E. Vargiu, J.A. Lorenzo Fernandez, and F. Miralles}, ``Real-Time 2D Face Detection and Features-based Tracking in Video'', \textit{IADIS Multi Conference in Computer Science in Computer Graphics, Visualization, Computer Vision and Image Processing 2012}. Lisbon: Portugal (Jul. 2012), 2012.
\item \textbf{J. Cartwright, N. Johnson, B. Davis, Z. Qiang, T.L. Bravo, A. Enoch, G. Lemaitre, H. Roth, and Y. Petillot}, ``Nessie III Autonomous Underwater Vehicle for SAUC-E 2008'', \textit{The Unmanned Underwater Vehicle Showcase (UUVS)}, 2008.
\end{enumerate}

\underline{\textit{Thesis:}}

\begin{enumerate}
\item \textbf{G. Lemaitre and P.M. Walker}, ``Absolute Quantification in 1H MRSI of the Prostate at 3T'', \textit{Thesis for Master in Science Vision and roBOTic (ViBOT)}, 2011.
\item \textbf{G. Lemaitre, A. Bikfalvi, and J. Llach}, ``Valorisation of Computerized Technology in the Health Care Sector'', \textit{Thesis for Master in Science Business Innovation and Technology Management (BITM)}, 2014.
\end{enumerate}

}